Download data

### 2024-05-08 scripts/subsetDataforCrews.Rmd
workable prototype for provisional stzs

emps <- filter(seed_zones, stz == 'DesertSW' & Requisition == 'Uncompahgre - P102085') %>% 
  pull(binomial) %>% 
  unique()

spp_needed_test <- filter(spp_needed, Requisition == 'Uncompahgre - P102085' & binomial %in% emps)
spp_needed_test <- split(spp_needed_test, f = spp_needed_test$binomial)

example_rast <- rast(spp_needed_test[[1]][,'path_raw_sdm'])
ptest <- project(prov_stz[[2]], 'epsg:5070')
ptest <- resample(ptest, example_rast)

#### Process geographic data to a mask of the field office ####
focal_bbox <- dplyr::filter(admin_boundaries, ADMU_NA %in% stringr::str_to_upper(teams_list[[13]]$FieldOffice) ) %>%  
  sf::st_union() %>% 
  sf::st_transform(5070)

focal_bbox <- focal_bbox 
blm_surf_sub <- sf::st_intersection(blm_surf, focal_bbox)

ptest <- mask(ptest, blm_surf_sub)
ptest <- trim(ptest)
plot(ptest)

crew_dir <-  '/media/steppe/hdd/2024SOS_CrewGeospatial/Uncompahgre - P102085'
lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, 
            seed_zones = seed_zones, pSTZs = ptest) # 24 pts, 245 polys

>>>>

p <- '/media/steppe/hdd/SDM_restorations/results/suitability_maps'
example_rast <- rast(file.path(p,'Achnatherum_hymenoides1k-2024-01-10_09:42:26.tif') )
prov_stz <- project(prov_stz, 'epsg:5070') 
prov_stz <- resample(prov_stz, example_rast)

lapply( 
  teams_list[2], project_maker, 
  admu = admin_boundaries, 
  target_species = spp_needed, 
  blm_surf = blm_surf, 
  fs_surf = usfs_surf, 
  fire = fire_perimeters, 
  invasive = invasives, 
  total_change = change_intensity,  
  occurrences = occurrences, 
  roads = roads,  
  pSTZs = prov_stz, 
  seed_transfer = STZ
  )

plot(ob[["Bishop - P102079"]][["10"]])
